### 2012-11-28 inst/examples/reed-example.Rmd
Compare GP to Reed optimum for BH (successful run this time)

```{r}
library(kernlab)
#gp <- gausspr(obs$x, obs$y, kernel="rbfdot", kpar=list(sigma=0.5), fit=FALSE, scaled=FALSE, var=.09)
gp <- gausspr(obs$x, obs$y, kernel="rbfdot", scaled=FALSE, var=sigma_g^2)
Ef <- predict(gp, X)
```

>>>>

```{r}
library(kernlab)
#gp <- gausspr(obs$x, obs$y, kernel="rbfdot", kpar=list(sigma=0.5), fit=FALSE, scaled=FALSE, var=.09)
gp <- gausspr(obs$x, obs$y, kernel="rbfdot", scaled=FALSE, var = sigma_g^2)
Ef <- predict(gp, X)
```
